Approximating the Optimal State Abstraction

### 2015-10-07 state_abstraction.tex
beep
updated section 2

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\input{../p.tex}
\title{Approximating the Optimal State Abstraction}
\author{}
\date{}                                           % Activate to display a given date or no date

@@

% --- SECTION: Motivation ---
\newpage
\section{Background}

@@

\vspace{4mm}
\elem{For example:}
Historically, we'ved relied on OO-MDPs a lot. There are other possible representations one might consider to collapse our representation of the real world. Objects seem like a reasonable choice given how object-oriented the human experience seems to be.

@@

% Subsection: Arbitrary reduction in Sample Complexity
\subsection{Result 1: Arbitrary reduction in Sample Complexity}
First: Grid example that goes from NxM to N, (always go up, no down action).

\subsection{Result 2: With a perfect abstractor, consider the exploration problem}

\subsection{Result 3: Collapsing on {\it just state variables} is insufficient to preserve any kind of optimality}

\subsection{Elephant in the Room}
Q: But what's the elephant in the room with all of this?
A: Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
A: Furthermore, we need to know something about the optimal behavior in advance!

@@

Future Work:
\begin{itemize}
\item Learning $\phi$
\item Connection to AMDPs (e.g. consider $\Omega : \langle S, A, R, T, \gamma \rangle \mapsto \langle S', A', R', T', \gamma' \rangle$
\item Connection to teaching.
\end{itemize}

>>>>

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\input{p.tex}
\title{Approximating the Optimal State Abstraction}
\author{}
\date{}                                           % Activate to display a given date or no date

@@

% --- SECTION: Background ---
\newpage
\section{Background}

@@

\vspace{4mm}
\elem{For example:}
Historically, we've relied on OO-MDPs a lot. There are other possible representations one might consider to collapse our representation of the real world. Objects seem like a reasonable choice given how object-oriented the human experience seems to be.

@@

\elem{Basic Point:} State abstraction for planning, learning, possibly bandits could be EPIC.

% Subsection: Arbitrary reduction in Sample Complexity for a specific MDP.
\subsection{Result 1: Arbitrary reduction in Sample Complexity for a particular MDP.}

% Subsection: More general SC reduction result.
\subsection{Result 2: More general result about sample complexity reduction for MDPs of a certain type}

Q: Assuming a given MDP has property set X, can we say anything about the possible reduction in sample complexity using a state abstraction function.

% Maybe something about exploration.

% Subsection: Things you should not compress on.
\subsection{Result 3: Collapsing on just {\it state variables}, or {\it reward}, or {\it other?} is insufficient to preserve any kind of optimality (including $\epsilon$-optimality.}

% --- SECTION: Elephants In the Room ---
\section{Elephants in the Room}

\begin{itemize}
\item Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
\item Can't capture temporal abstraction.
\end{itemize}

@@

Future Work:
\begin{itemize}
\item Learning $\phi$
\item Connection to AMDPs (e.g. consider $\Omega : \langle S, A, R, T, \gamma \rangle \mapsto \langle S', A', R', T', \gamma' \rangle$
\item Connection to teaching.
\begin{itemize}
\item AMDPs seem well suited to hierarchical teaching Carl-style.
\item Problem: once solved for optimal policy in AMDP already solved in low level state. Probably want to set up teaching to avoid this.
\end{itemize}
\end{itemize}
